a pipeline to analyse time-course gene expression data

### 2019-02-19 scripts/00_introduction.Rmd
DOC More details on the data set used

---
title: "XXX: a pipeline to analyse time-course gene expression data"
output: html_document
---

@@

This workflow is illustrated using data from a micro-array time-course
experiment, exposing mice to different strains of influenza, and collecting
lung tissue during 12 time-points (..).

>>>>

---
title: "a pipeline to analyse time-course gene expression data"
output: html_document
---

@@

This workflow is illustrated using data from a micro-array time-course
experiment, exposing mice to three different strains of influenza, and
collecting lung tissue during 14 time-points.  The three strains of influenza
used in the study are (1) a low pathogenicity seasonal H1N1 influenza virus
(A/Kawasaki/UTK4/2009 [H1N1]), a mildly pathogenic virus from the 2009
pandemic season (A/California/04/2009 [H1N1]), and a highly pathogenic H5N1
avian influenza virus (A/Vietnam/1203/2004 [H5N1]. Mice were injected with
10^5 PFU of each virus. An adidtional 42 mice were injected with a lower dose
of the Vietnam avian influenza virus (10^3 PFU).

XXX Add summary of the findings of the paper.
